Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-03-16 ms/ms08_figures.tex
MS
ENH

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 1: Histogram of percentage of explained of GWAS
% Fig 2: ucsc screenshots
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \begin{subfigure}[]{0.32\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_perc_tophits_eqtl.py/hist_perc_tophits_eqtl_excl_mhc.png}
    \end{subfigure}

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{fig/ucsc_gwas2eqtl_il4_bcell.png}
    \end{subfigure}

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{fig/ucsc_gwas2eqtl_il4_monocyte.png}
    \end{subfigure}

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{fig/ucsc_gwas2eqtl_il4_frontalcortex.png}
    \end{subfigure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 1: Histogram of percentage of explained of GWAS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

        \includegraphics[width=0.5\textwidth]{\floatRelativePath/plthst_perc_tophits_eqtl.py/hist_perc_tophits_eqtl_excl_mhc.png}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 2: ucsc screenshots
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{fig/ucsc_gwas2eqtl_il4_bcell_help.png}
    \end{subfigure}

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{fig/ucsc_gwas2eqtl_il4_monocyte.png}
    \end{subfigure}

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{fig/ucsc_gwas2eqtl_il4_frontalcortex.png}
    \end{subfigure}
